STAT 450 Project: Real Estate

### 2020-04-08 doc/450/RealEstate_final_report.Rmd
final report RMD, pdf, supported file added

---
title: 'STAT 450 Project: Real Estate'
author: "Peter Han, Xuechun Lu, Yuetong Liu, Yuting Wen"
date: "30/03/2020"
output:
  pdf_document
---

@@

```{r, message=F, warning=F, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(here)
library(readxl)
library(broom)
library(glmnet)
library(dummies)
set.seed(123)
```

@@

The main objective of our project is to accurately predict future mill rate (property tax) in metro Vancouver for the following 3 property tax classes: Tax class 1: Residential, Tax class 5: Light industry and Tax class 6: Business and other. Data cleaning, exploratory data analysis are used in this project to analyze the relationship between mill rate and other factors. Data cleaning is performed to aggregate our data into summary statistics. Exploratory analysis shows that there are strong relationships between mill rate and tax class and mill rate and municipalities; it also shows there is a fairly strong correlation between mill rate and average assessment per property in different municipalities. *Ordinary linear model*, *reduced ordinary linear model*, *Ridge Regression* and *LASSO* are used to predict the mill rate. A full assessment of the performance - prediction power and goodness of fit of these models, is shown below.

@@

Our client provides us with the past 5 years' property assessment data in BC. Since the only interest is in predicting mill rate for metro Vancouver and specific tax classes, a subset of properties that satisfy our interest have been selected:

@@

To reduce the dimension of our data, all properties in the same region, tax class code, and year are aggregated into a group because these properties have the same mill rate,  which is our response variable. Here is the summary statistics for these groups:

- Mill rate (rate)
- Total Assessment (assessTotal)
- Total Land Assessment (landTotal)
- Total Improvement Assessment (improvementTotal)
- Total number of properties (propertyCount)
- Tax Class Code (TaxClassCode)
- Municipality (AddressAssessorMunicipalityDesc)
- Year

@@

Before any prediction on the future mill rate of Metro Vancouver’s real estate market was made, exploratory data analysis was performed to explore and visualize the main characteristics of our dataset. Correlation analyses between Mill Rate and Total Assessment, Mill Rate and Total Land Assessment, and Mill Rate and Total Improvement Assessment were performed. From our initial analysis, outliers in municipalities were found. Data transformation - calculating the average total assessment, was used to reduce the effect of outliers.

@@

The full linear model (*ORL full*) was built first. TaxClassCode, Municipalities, assessTotal, landTotal, improvementTotal and propertyCount were considered in this model. Based on the results of EDA, a list of significant variables were selected and included in another linear model (*OLR transformed*). To compare the effect of linear models with and without features, a null model (*OLR null*) with no features used, was also constructed.

@@

Other than ordinary linear regressions, we are also interested in the performance of more advanced linear regressions like *Ridge* and *Lasso*. *Ridge* and *Lasso* have different objective functions to optimize; they take penalties in the sum of absolute values and sum of squared absolute values of weights respectively. A reason to consider Ridge Regression is that it helps deal with multicollinearity of the explanatory variables. This might be relevant to our study as some features used in this study are correlated (assessTotal, landTotal and improvementTotal). Lasso Regression is also included in this study because it does variable selections automatically by imposing a constraint on model parameters that may possibably causes some regression coefficients to shrink to zero.

@@

Since the mill rate is mainly affected by the total assessment, which is the sum of total land assessment and total improvement assessment, scatter plots between mill rate and total assessment among different municipalities is created to show the relationship in Figure 1. Each color in the figure belongs to three tax classes of one municipality.

Scatter plots between mill rate and total land assessment, mill rate and total improvement assessment are similar to Figure 1. For more details about them, please refer to **Appendix**.

@@

# rename column for better visulization
assessment_eda <- assessment_transform
names(assessment_eda)[2] <- paste("Municipality")
names(assessment_eda)[3] <- paste("Tax Class")
names(assessment_eda)[4] <- paste("Total Assessment")
names(assessment_eda)[5] <- paste("Total Land Assessment")
names(assessment_eda)[6] <- paste("Total Improvement Assessment")
names(assessment_eda)[8] <- paste("Mill Rate")
names(assessment_eda)[9] <- paste("Average Total Assessment")

assessment_eda %>%
   ggplot(aes(x=`Total Assessment`,
              y=`Mill Rate`,group=Municipality,
              color=Municipality)) + 
   geom_point() + 
   ggtitle(sprintf("Figure 1: Mill Rate vs Total Assessment")) + 
   geom_smooth(aes(group = 1), size = 0.5, method = "glm", se = FALSE, colour = "black") +
   theme(plot.background = element_rect(fill = "darkgrey"), legend.key.size = unit(0.2, "cm"))
```

There is no clear trend between the mill rate and total assessment from Figure 1. The plot has also shown that most points are condensed on the left horizontal axis since some municipalities have larger assessment values than others.

To reduce the effect of large assessment in some municipalities, total assessment across all municipalities is transformed by taking total assessment dividing by the number of properties of each municipality and tax class. The transformed data is named **"Average Total Assessment"**. A scatter plot between mill rates and average total assessments is shown in Figure 2.

```{r, echo=FALSE}
assessment_eda %>%
 ggplot(aes(x=`Average Total Assessment`,
            y=`Mill Rate`,group=Municipality,
            color=Municipality)) + 
 geom_point() + 
 ggtitle(sprintf("Figure 2: Mill rate v.s. Average Total Assessment")) + 
 geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black") +
theme(plot.background = element_rect(fill = "darkgrey"), legend.key.size = unit(0.2, "cm"))
```

The plot from Figure 2 has shown that the mill rate tends to decrease as the average total assessment increase. Also, they have a moderately strong linear correlation.

@@

Here categorical variables are taken into account, boxplots of mill rate across municipalities and tax classes are plotted to display the distributions in Figure 3 and Figure 4, respectively.

```{r, echo=FALSE}
# ______________________________________________________________________________________________
# CATEGORICAL variables
assessment_eda %>%
     ggplot(aes(x=Municipality,
                y=`Mill Rate`,fill=Municipality)) + 
     geom_boxplot() + 
     ggtitle(sprintf("Figure 3: Mill rate across Municipalities")) +
     theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
```

```{r, echo=FALSE}
assessment_eda %>%
     ggplot(aes(x=as.factor(`Tax Class`),
                y=`Mill Rate`,fill=`Tax Class`)) + 
     geom_boxplot() + 
     ggtitle(sprintf("Figure 4: Mill rate across Tax Classes")) +
     theme(legend.position = "none") +
     labs(x="Tax Class") +
     scale_x_discrete(labels=c("1", "5", "6"))
```

Figure 3 has shown that most municipalities have different mean and variance in terms of mill rates.

Figure 4 has also supported that there is unequal mean and variance across tax classes.

@@

The results of Kruskal-Wallis Test is shown in Table 1.

        Table 1: Kruskal-Wallis Test of Mill Rate across Municipality and Tax Class

Distribution  | p-value
------|--------
Mill Rate across Municipality | 0.00675
Mill Rate across Tax Class | < 2.2e-16

The p-values in Table 1 have supported that there are nonidentical distributions of mill rates across municipalities and tax classes.

@@

@@

The distributions of the goodness of fit and prediction power across models are displayed in Figure 5 and Figure 6, respectively, the distribution of null model is removed since it has larger values compared to all other models.

The distributions of MSPE on the training sets and test sets across all models are also displayed in Table 3 and Table 4 respectively.

@@

  # prediction power
  mspe.ri[i]<-mean((y - pr.ri)^2)
  mspe.la[i]<-mean((y - pr.la)^2)
  mspe.reduced[i]<-mean((y - pr.reduced)^2)
  mspe.f[i]<-mean((y - pr.f)^2)
  mspe.n[i]<-mean((y - pr.n)^2)
}

boxplot(mspe1.la, 
        mspe1.ri, 
        mspe1.reduced, 
        mspe1.f, 
        names = c("LASSO", 
                  "Ridge",
                  "Transformed", 
                  "Full"
                  ), 
        col = c("steelblue","gray80",
                "pink", 
                "tomato"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 1,
        main = " Figure 7: Goodness of Fit",
        ylab = expression(hat(MSPE)))
```

                          Table 2: Goodness of fit of All Models

Model | PMSE:Min | PMSE:Mean | PMSE:Max
-----|-----|-----|-----|
Full Model | 5.23 | 5.43 | 5.52 |
Transformed Model | 4.45 | 4.59 | 4.64 |
Null Model | 36.33 | 36.52 | 36.64 |
Lasso for Full Model | 4.52 | 4.63 | 4.73 |
Ridge Regression for Full Model | 4.50 | 4.63 | 4.72 |

```{r, warning=FALSE, echo=FALSE}
boxplot(mspe.la, 
        mspe.ri,
        mspe.reduced, 
        mspe.f,
        names = c("LASSO", 
                  "Ridge", 
                  "Transformed", 
                  "Full"
                  ), 
        col = c("steelblue","gray80", 
                "pink",
                "tomato"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 1,
        main = "Figure 8: Prediction Power",
        ylab = expression(hat(MSPE)))
```

                            Table 3: Prediction Power of All Models

Model | PMSE:Min | PMSE:Mean | PMSE:Max
-----|-----|-----|-----|
Full Model | 6.50 | 6.97 | 7.59 |
Transformed Model | 5.60 | 5.92 | 6.51 |
Null Model | 36.67 | 36.87 | 37.26 |
Lasso for Full Model | 5.58 | 5.91 | 6.40 |
Ridge Regression for Full Model | 5.53 | 5.88 | 6.39 |

@@

For predicted mill rate in 2020, please refer to **Appendix** Table 4.

@@

@@

```{r, echo=FALSE}
assessment_eda %>%
   ggplot(aes(x=`Total Land Assessment`,
              y=`Mill Rate`,group=Municipality,
              color=Municipality)) + 
   geom_point() + 
   ggtitle(sprintf("Figure 7: Mill Rate vs Total Land Assessment")) + 
   geom_smooth(aes(group = 1), size = 0.5, method = "glm", se = FALSE, colour = "black") +
   theme(plot.background = element_rect(fill = "darkgrey"), legend.key.size = unit(0.2, "cm"))
```

@@

```{r, echo=FALSE}
assessment_eda %>%
   ggplot(aes(x=`Total Improvement Assessment`,
              y=`Mill Rate`,group=Municipality,
              color=Municipality)) + 
   geom_point() + 
   ggtitle(sprintf("Figure 8: Mill Rate vs Total Improvement Assessment")) + 
   geom_smooth(aes(group = 1), size = 0.5, method = "glm", se = FALSE, colour = "black") +
   theme(plot.background = element_rect(fill = "darkgrey"), legend.key.size = unit(0.2, "cm"))
```

@@

                Table 4: Predicted Mill Rate in 2020 based on transformed model (%)

Municipality | Residential (%) | Light industry (%) | Business (%)                      
------|------|------|------
Anmore | 0.98 | NA | 9.91
Belcarra | 1.19 | NA | 12.31
Bowen Island | 1.63 | 14.69 | 11.15
Burnaby | -2.76 | 12.80 | 10.88
Coquitlam | 1.72 | 17.70 | 12.84
Delta | 5.50 | 12.98 | 13.65
Langley - City | 1.73 | 15.12 | 12.25
Langley - Township | 3.77 | 12.46 | 12.49
Lions Bay | 2.19 | NA | 11.66
Maple Ridge | 5.11 | 16.88 | 13.60
New Westminster | 4.65 | 18.04 | 15.78
North Vancouver - City | -2.17 | 15.51 | 11.90
North Vancouver - Dist | 1.29 | 13.68 | 11.82
Pitt Meadows | 6.06 | 17.00 | 13.78
Port Coquitlam | 4.91 | 17.58 | 14.50
Port Moody | 4.16 | 17.66 | 13.44
Richmond | 1.14 | 10.42 | 10.29
Surrey | 0.82 | 12.47 | 10.53
Vancouver | 2.69 | 12.38 | 8.79
West Vancouver | 4.92 | 17.05 | 12.62
White Rock | 1.88 | 16.33 | 12.17

@@

                          Table 5: Data with missing mill rate

Year  | Region | Class |Number of Properties
------|--------|-------|----------
2016 | Belcarra | 06 | 9 
2016 | Lions Bay | 01 | 40 
2016 | Lions Bay | 06 | 25 
2016 | Maple Ridge Rural | 05 | 36 
2017 | Belcarra | 06 | 9 
2017 | Lions Bay | 01 | 39 
2017 | Lions Bay | 06 | 24 
2017 | Maple Ridge Rural | 05 | 36 
2018 | Maple Ridge Rural | 05 | 36 
2019 | Maple Ridge Rural | 05 | 38

>>>>

---
title: 'STAT 450 Project: Real Estate'
author: "Peter Han, Xuechun Lu, Yuetong Liu, Yuting Wen"
date: "07/04/2020"
output: 
  rmarkdown::pdf_document:
    fig_caption: yes        
    includes:  
      in_header: my_header.tex
---

@@

```{r, message=F, warning=F, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(here)
library(readxl)
library(broom)
library(glmnet)
library(dummies)
library(scales)
set.seed(123)
```

@@

The main objective of our project is to accurately predict future mill rate (property tax) in metro Vancouver for the following 3 property tax classes: Tax class 1: Residential, Tax class 5: Light industry and Tax class 6: Business and other. Data cleaning, exploratory data analysis are used in this project to analyze the relationship between mill rate and other factors. Data cleaning is performed to aggregate our data into summary statistics. Exploratory analysis shows that there are strong relationships between mill rate and tax class and mill rate and municipalities; it also shows there is a fairly strong correlation between mill rate and average assessment per property in different municipalities. *Ordinary linear model*, *reduced ordinary linear model*, *Ridge Regression* and *LASSO* are used to predict the mill rate. A full assessment of the performance --- prediction power and goodness of fit of these models, is shown below.

@@

Our client provided us with the past 5 years' property assessment data in BC. Since the only interest is in predicting mill rate for metro Vancouver and specific tax classes, a subset of properties that satisfy our interest have been selected:

@@

To reduce the dimension of our data, all properties in the same region, tax class code, and year are aggregated into a group because these properties have the same mill rate,  which is our response variable. Here are the summary statistics for these groups:

- Mill rate (rate)
- Total Assessment (assessTotal)
- Total Land Assessment (landTotal)
- Total Improvement Assessment (improvementTotal)
- Total Number of Properties (propertyCount)
- Tax Class Code (TaxClassCode)
- Municipality (AddressAssessorMunicipalityDesc)

@@

Before any prediction on the future mill rate of Metro Vancouver’s real estate market was made, exploratory data analysis was performed to explore and visualize the main characteristics of our dataset. Correlation analyses between Mill Rate and Total Assessment, Mill Rate and Total Land Assessment, and Mill Rate and Total Improvement Assessment were performed. From our initial analysis, outliers in municipalities were found. Data transformation --- calculating the average total assessment, was used to reduce the effect of outliers.

@@

The full linear model (*OLR full*) was built first. TaxClassCode, Municipalities, assessTotal, landTotal, improvementTotal and propertyCount were considered in this model. Based on the results of EDA, a list of significant variables were selected and included in another linear model (*OLR transformed*), as shown in **Table 2**. To compare the effect of linear models with and without features, a null model (*OLR null*) with no features used, was also constructed.

Refer to **Appendix** for variables selected in both *OLR full* and *OLR transformed* models.

@@

Other than ordinary linear regressions, we are also interested in the performance of more advanced linear regressions like *Ridge* and *Lasso*. *Ridge* and *Lasso* have different objective functions to optimize; they take penalties in the sum of absolute values and sum of squared absolute values of weights respectively. A reason to consider Ridge Regression is that it helps deal with multicollinearity of the explanatory variables. This might be relevant to our study as some features used in this study are correlated (assessTotal, landTotal and improvementTotal). Lasso Regression is also included in this study because it does variable selections automatically by imposing a constraint on model parameters that may possibly cause some regression coefficients to shrink to zero.

@@

Since the mill rate is mainly affected by the total assessment, which is the sum of total land assessment and total improvement assessment, scatter plots between mill rate and total assessment among different municipalities is created to show the relationship in **Figure 1**. Each color in the figure belongs to three tax classes of one municipality.

Scatter plots between mill rate and total land assessment, mill rate and total improvement assessment are similar to **Figure 1**. For more details about them, please refer to **Appendix**.

@@

# rename column for better visulization
assessment_eda <- assessment_transform
names(assessment_eda)[2] <- paste("Municipality")
names(assessment_eda)[3] <- paste("Tax Class")
names(assessment_eda)[4] <- paste("Total Assessment")
names(assessment_eda)[5] <- paste("Total Land Assessment")
names(assessment_eda)[6] <- paste("Total Improvement Assessment")
names(assessment_eda)[8] <- paste("Mill Rate")
names(assessment_eda)[9] <- paste("Average Total Assessment")
```

```{r, echo=FALSE, fig.cap="Mill Rate vs Total Assessment"}
assessment_eda %>%
   ggplot(aes(x=`Total Assessment`,
              y=`Mill Rate`,group=Municipality,
              color=Municipality)) + 
   geom_point() + 
  xlab("Total Assessment (in Billion)") +
   geom_smooth(aes(group = 1), size = 0.5, method = "glm", se = FALSE, colour = "black") +
  scale_x_continuous(labels = unit_format(unit = "Billion", scale = 1e-9))
```

There is no clear trend between the mill rate and total assessment from **Figure 1**. The plot has also shown that most points are condensed on the left horizontal axis since some municipalities have larger assessment values than others.

To reduce the effect of large assessment in some municipalities, total assessment across all municipalities is transformed by taking total assessment dividing by the number of properties of each municipality and tax class. The transformed data is named **"Average Total Assessment"**. A scatter plot between mill rates and average total assessments is shown in **Figure 2**.

```{r, echo=FALSE, fig.cap="Mill rate v.s. Average Total Assessment"}
assessment_eda %>%
 ggplot(aes(x=`Average Total Assessment`,
            y=`Mill Rate`,group=Municipality,
            color=Municipality)) + 
 geom_point() + 
  xlab("Average Total Assessment (in Million)") +
 geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black") +
  scale_x_continuous(labels = unit_format(unit = "Million", scale = 1e-6))
```

The plot from **Figure 2** has shown that the mill rate tends to decrease as the average total assessment increase. Also, they have a moderately strong linear correlation.

@@

Here categorical variables are taken into account, boxplots of mill rate across municipalities and tax classes are plotted to display the distributions in **Figure 3** and **Figure 4**, respectively.

```{r, echo=FALSE,fig.cap="Mill rate across Municipalities"}
# ______________________________________________________________________________________________
# CATEGORICAL variables
assessment_eda %>%
     ggplot(aes(x=Municipality,
                y=`Mill Rate`,fill=Municipality)) + 
     geom_boxplot() + 
     theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none", axis.title.x=element_blank())
```

```{r, echo=FALSE, fig.cap="Mill rate across Tax Classes", fig.width=6,fig.height=3}
assessment_eda %>%
     ggplot(aes(x=as.factor(`Tax Class`),
                y=`Mill Rate`,fill=`Tax Class`)) + 
     geom_boxplot() + 
     theme(legend.position = "none", axis.title.x=element_blank()) +
     scale_x_discrete(labels=c("Residential (1)", "Light industry (5)", "Business and other (6)"))
```

**Figure 3** has shown that most municipalities have different mean and variance in terms of mill rates.

**Figure 4** has also supported that there is unequal mean and variance across tax classes.

@@

The results of Kruskal-Wallis Test is shown in **Table 1**.

| Distribution  | p-value |
| :------------ | :-----------: | 
| Mill Rate across Municipality | 0.00675 |
| Mill Rate across Tax Class | < 2.2e-16 |

Table: Kruskal-Wallis Test of Mill Rate across Municipality and Tax Class

The p-values in **Table 1** have supported that there are nonidentical distributions of mill rates across municipalities and tax classes.

@@

In conclusion, Average Total Assessment, Tax Class Code and Municipality are selected to fit another linear model, named **OLR transformed**. Refer to **Appendix** for more detail.

@@

The distributions of the goodness of fit and prediction power across models are displayed in **Figure 5** and **Figure 6**, respectively, the distribution of null model is removed since it has larger values compared to all other models.

The distributions of MSPE on the training sets and test sets across all models are also displayed in **Table 2** and **Table 3** respectively.

@@

  # prediction power
  mspe.ri[i]<-mean((y - pr.ri)^2)
  mspe.la[i]<-mean((y - pr.la)^2)
  mspe.reduced[i]<-mean((y - pr.reduced)^2)
  mspe.f[i]<-mean((y - pr.f)^2)
  mspe.n[i]<-mean((y - pr.n)^2)
}
```

```{r, warning=FALSE, echo=FALSE, fig.cap="Goodness of Fit"}
boxplot(mspe1.la, 
        mspe1.ri, 
        mspe1.reduced, 
        mspe1.f, 
        names = c("LASSO", 
                  "Ridge",
                  "Transformed", 
                  "Full"
                  ), 
        col = c("steelblue","gray80",
                "pink", 
                "tomato"), 
        cex.axis = 1, 
        cex.lab = 1, 
        ylab = expression(hat(MSPE)))
```

| Model | PMSE:Min | PMSE:Mean | PMSE:Max |
| :-----: | :-----: | :-----: | :-----: |
| Full Model | 5.23 | 5.43 | 5.52 |
| Transformed Model | 4.45 | 4.59 | 4.64 |
| Null Model | 36.33 | 36.52 | 36.64 |
| Lasso for Full Model | 4.52 | 4.63 | 4.73 |
| Ridge Regression for Full Model | 4.50 | 4.63 | 4.72 |

Table: Goodness of fit of All Models

```{r, warning=FALSE, echo=FALSE, fig.cap="Prediction Power"}
boxplot(mspe.la, 
        mspe.ri,
        mspe.reduced, 
        mspe.f,
        names = c("LASSO", 
                  "Ridge", 
                  "Transformed", 
                  "Full"
                  ), 
        col = c("steelblue","gray80", 
                "pink",
                "tomato"), 
        cex.axis = 1, 
        cex.lab = 1, 
        ylab = expression(hat(MSPE)))
```

| Model | PMSE:Min | PMSE:Mean | PMSE:Max |
| :-----: | :-----: | :-----: | :-----: |
| Full Model | 6.50 | 6.97 | 7.59 |
| Transformed Model | 5.60 | 5.92 | 6.51 |
| Null Model | 36.67 | 36.87 | 37.26 |
| Lasso for Full Model | 5.58 | 5.91 | 6.40 |
| Ridge Regression for Full Model | 5.53 | 5.88 | 6.39 |

Table: Prediction Power of All Models

@@

For predicted mill rate in 2020, please refer to **Appendix** **Table 6**.

@@

### Variables selected in different models

| Parameter  | Type | 
| :------------ | :-----------: | 
| Total Assessment     | Quantitative   | 
| Total Land Assessment     | Quantitative   | 
| Total Improvement Assessment     | Quantitative   | 
| Total Number of Properties     | Quantitative   | 
| Tax Class Code     | Categorical  | 
| Municipality       | Categorical |

Table: Selected Explanatory Variables of OLR full

*Ridge Regression* and *Lasso* models were fitted based on *OLR full* model.

| Parameter  | Type | 
| :------------ | :-----------: | 
| Average Total Assessment     | Quantitative   | 
| Tax Class Code     | Categorical  | 
| Municipality       | Categorical |

Table: Selected Explanatory Variables of OLR transformed

@@

```{r, echo=FALSE, fig.cap="Mill Rate vs Total Land Assessment",fig.width=6,fig.height=4}
assessment_eda %>%
   ggplot(aes(x=`Total Land Assessment`,
              y=`Mill Rate`,group=Municipality,
              color=Municipality)) + 
   geom_point() + 
  xlab("Total Land Assessment (in Billion)") +
   geom_smooth(aes(group = 1), size = 0.5, method = "glm", se = FALSE, colour = "black") +
  scale_x_continuous(labels = unit_format(unit = "B", scale = 1e-9))
```

@@

```{r, echo=FALSE, fig.cap="Mill Rate vs Total Improvement Assessment",fig.width=6,fig.height=4}
assessment_eda %>%
   ggplot(aes(x=`Total Improvement Assessment`,
              y=`Mill Rate`,group=Municipality,
              color=Municipality)) + 
   geom_point() + 
  xlab("Total Improvement Assessment (in Billion)") +
   geom_smooth(aes(group = 1), size = 0.5, method = "glm", se = FALSE, colour = "black") +
  scale_x_continuous(labels = unit_format(unit = "Billion", scale = 1e-9))
```

@@

| Municipality | Residential (%) | Light industry (%) | Business (%) |                    
| :------: | :------: | :------: | :------: |
| Anmore | 0.98 | NA | 9.91 |
| Belcarra | 1.19 | NA | 12.31 |
| Bowen Island | 1.63 | 14.69 | 11.15 |
| Burnaby | -2.76 | 12.80 | 10.88 |
| Coquitlam | 1.72 | 17.70 | 12.84 |
| Delta | 5.50 | 12.98 | 13.65 |
| Langley - City | 1.73 | 15.12 | 12.25 |
| Langley - Township | 3.77 | 12.46 | 12.49 |
| Lions Bay | 2.19 | NA | 11.66 |
| Maple Ridge | 5.11 | 16.88 | 13.60 |
| New Westminster | 4.65 | 18.04 | 15.78 |
| North Vancouver - City | -2.17 | 15.51 | 11.90 |
| North Vancouver - Dist | 1.29 | 13.68 | 11.82 |
| Pitt Meadows | 6.06 | 17.00 | 13.78 |
| Port Coquitlam | 4.91 | 17.58 | 14.50 |
| Port Moody | 4.16 | 17.66 | 13.44 |
| Richmond | 1.14 | 10.42 | 10.29 |
| Surrey | 0.82 | 12.47 | 10.53 |
| Vancouver | 2.69 | 12.38 | 8.79 |
| West Vancouver | 4.92 | 17.05 | 12.62 |
| White Rock | 1.88 | 16.33 | 12.17 |

Table: Predicted Mill Rate in 2020 based on transformed model

@@

| Year  | Region | Class | Number of Properties |
| :------: | :--------: | :-------: | :----------: |
| 2016 | Belcarra | 06 | 9 |
| 2016 | Lions Bay | 01 | 40 | 
| 2016 | Lions Bay | 06 | 25 |
| 2016 | Maple Ridge Rural | 05 | 36 |
| 2017 | Belcarra | 06 | 9 |
| 2017 | Lions Bay | 01 | 39 |
| 2017 | Lions Bay | 06 | 24 |
| 2017 | Maple Ridge Rural | 05 | 36 |
| 2018 | Maple Ridge Rural | 05 | 36 |
| 2019 | Maple Ridge Rural | 05 | 38 |

Table: Data with missing mill rate
